Bayesian hidden Markov model analysis of single-molecule force spectroscopy:\\ Characterizing kinetics under measurement uncertainty

### 2015-02-16 manuscripts/bayesian-hmm-method/bhmm.tex
Fix to make figure captions in sans serif.

% Rework captions to use sans serif font.
\makeatletter
\renewcommand\@make@capt@title[2]{%
 \@ifx@empty\float@link{\@firstofone}{\expandafter\href\expandafter{\float@link}}%
  {\textbf{#1}}\sf\@caption@fignum@sep#2\quad
}%
\makeatother

@@

\begin{figure*}[tb]
\noindent
\resizebox{\textwidth}{!}{\includegraphics{algorithm-workflow/Fig_ProbabilitySpace_trimmed.pdf}}
\caption{{\bf Illustration of the Bayesian hidden Markov model (BHMM) sampling algorithm.}
During each BHMM update, a modified forward-backward algorithm is used to sample a new hidden state trace $\mathbf{S}$, which is then used to generate a new sample of the reversible transition matrix $\mathbf{T}$ using MCMC sampling, followed by sapling of the state emission probabilities $\mathbf{E}$.
The cycle then repeats for each subsequent iteration, which together sample from the Bayesian posterior of the HMM and fully characterize the uncertainty in the kinetic model given the data.
\label{figure:bhmm-workflow}}
\end{figure*}

>>>>

% Rework captions to use sans serif font.
\makeatletter
\renewcommand\@make@capt@title[2]{%
 \@ifx@empty\float@link{\@firstofone}{\expandafter\href\expandafter{\float@link}}%
  {\sf\textbf{#1}}\sf\@caption@fignum@sep#2\quad
}%
\makeatother

@@

\begin{figure*}[tb]
\noindent
\resizebox{0.8\textwidth}{!}{\includegraphics{algorithm-workflow/Fig_ProbabilitySpace.pdf}}
\caption{{\bf Illustration of the Bayesian hidden Markov model (BHMM) sampling algorithm.}
During each BHMM update, a modified forward-backward algorithm is used to sample a new hidden state trace $\mathbf{S}$, which is then used to generate a new sample of the reversible transition matrix $\mathbf{T}$ using MCMC sampling, followed by sapling of the state emission probabilities $\mathbf{E}$.
The cycle then repeats for each subsequent iteration, which together sample from the Bayesian posterior of the HMM and fully characterize the uncertainty in the kinetic model given the data.
\label{figure:bhmm-workflow}}
\end{figure*}
